---
title: "Homework 1"
author: Na Yun Cho
output: github_document
---

This is my solution to HW 1.

```{r}
library(tidyverse)
```


# Problem 1


**Create a data frame comprised of the specified elements.**

```{r}
prob1_df =
tibble(
  samp = rnorm(10),
  samp_gt_0 = samp > 0,
  char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
)
```


**Take the mean of each variable in my data frame.**

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

Conclusion: I can take the mean of numbers and logical but not character or factor.



**Convert variables to numeric variables.**

```{r}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```


**Convert vector types and multiply the random sample by the result.**
```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```



# Problem 2


**Load the penguins dataset.**

```{r}
data("penguins", package = "palmerpenguins")
```


**Write a short description of the penguins dataset using inline R code.**

The penguins dataset shows three different species of penguins and each of their location, bill length(mm), bill depth(mm), flipper length(mm), body mass(g), sex, and year of observation. 

The names of the variables in this dataset are `r names(penguins)`. 

In addition, the dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.

The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`mm. 

